Something something values disclosure replication

### 2022-07-06 paper/paper.Qmd
fix branches todo
overlooked merge issue?

```{r}
#| echo: false
#| label: tbl-bc
#| tbl-cap: "Regression analysis for hypotheses H2 (consumer risk sensitivity) and H3 (disclosure effect)"
bc_tbl = readRDS('out/03_bc_tbl.Rds')
bc_tbl
```

>>>>

```{r}
#| label: tbl-bc
#| tbl-cap: "Regression analysis for hypotheses H2 (consumer risk sensitivity) and H3 (disclosure effect)"
bc_tbl = readRDS(here(out_dir, '03_bc_tbl.Rds'))
bc_tbl
```
